---
title: "Additional Analyses (Public vs Private Sharing) - Study 1b"
output: html_notebook: default
---


```{r warning=FALSE, message=FALSE}
library(tidyverse)
library(brms)
library(future)
library(numform)
library(tidybayes)

rm(list = ls())

# Options
options(
  mc.cores = parallel::detectCores(),
  brms.backend = "cmdstanr",
  future.globals.maxSize = 2147483648
)
```


## Data
```{r}
# Load data
dl <- read_rds("../data/dl.rds")

# Calculate Post: Share Index
dl <- dl %>% mutate(
  post_share_index = (post_share_public + post_like_public + post_share_private + post_share_offline)/4,
  post_share_index_public = (post_share_public + post_like_public)/2
)

# Calculate Individualizing/Binding scores
dl <- dl %>% mutate(
  mfq_indi = (mfq_care + mfq_equa)/2,
  mfq_bind = (mfq_loya + mfq_auth + mfq_puri)/3
)

# Drop missing data
dl <- dl %>% drop_na(-headline_rating_true, -source_text)

# Assign new indices
dl <- dl %>% mutate(across(c(ii, kk, kk), ~as.integer(factor(.))))


# Standardize -------------------------------------------------------------

# Create data set for analyses
df <- dl %>% select(ii, jj, kk)

# Standardize person-level variables
df <- dl %>% 
  select(jj, starts_with("mfq_"), conservatism) %>% 
  distinct() %>% 
  mutate(
    across(-jj, list(z_jj = ~(. - mean(.))/sd(.)), .names = "{.fn}_{.col}")
  ) %>% 
  rename_with(~paste0("x_jj_", .), c(-jj, -starts_with("z_"))) %>% 
  left_join(df, ., by = "jj")

# Standardize headline-level variables
df <- dl %>% 
  select(kk, starts_with("headline_"), -headline_text) %>% 
  group_by(kk) %>% 
  dplyr::summarize(
    across(everything(), mean)
  ) %>% 
  mutate(
    across(-kk, list(z_kk = ~(. - mean(.))/sd(.)), .names = "{.fn}_{.col}")
  ) %>% 
  rename_with(~paste0("x_kk_", .), c(-kk, -starts_with("z_"))) %>% 
  left_join(df, ., by = "kk")
  
# Standardize post-level variables
df <- dl %>% 
  dplyr::select(
    ii, starts_with("post_"), 
    -post_sentiment, -post_framing, -post_text,
    -matches("share|like")
  ) %>% 
  group_by(ii) %>% 
  dplyr::summarize(
    across(everything(), mean)
  ) %>% 
  mutate(
    across(-ii, list(z_ii = ~(. - mean(.))/sd(.)), .names = "{.fn}_{.col}")
  ) %>% 
  rename_with(~paste0("x_ii_", .), c(-ii, -starts_with("z_"))) %>% 
  left_join(df, ., by = "ii")

# Standardize headline-/person-level variables
df <- dl %>% 
  select(ii, jj, kk, starts_with("headline_"), -headline_true, -headline_text) %>% 
  left_join(
    df %>% select(ii, jj, kk, starts_with("x_kk_")),
    by = c("ii", "jj", "kk")
  ) %>%
  mutate(
    z_headline_believable = headline_believable - x_kk_headline_believable,   
    z_headline_controversial = headline_controversial - x_kk_headline_controversial,   
    z_headline_surprising = headline_surprising - x_kk_headline_surprising,
    z_headline_interesting = headline_interesting - x_kk_headline_interesting, 
    z_headline_positive = headline_positive - x_kk_headline_positive
  ) %>% 
  mutate(
    across(starts_with("z_"), ~./sd(.))
  ) %>% 
  select(-starts_with("x_kk_")) %>% 
  rename_with(~paste0("x_", .), c(-ii, -jj, -kk, -starts_with("z_"))) %>% 
  left_join(df, ., by = c("ii", "jj", "kk"))

# Standardize post-/person-level variables
df <- dl %>% 
  select(
    ii, jj, kk,
    starts_with("post_"), 
    -post_sentiment, -post_framing, -post_text,
    -matches("share|like")
  ) %>% 
  left_join(
    df %>% select(ii, jj, kk, starts_with("x_ii_")),
    by = c("ii", "jj", "kk")
  ) %>%
  mutate(
    z_post_controversial = post_controversial - x_ii_post_controversial,
    z_post_surprising = post_surprising - x_ii_post_surprising,
    z_post_interesting = post_interesting - x_ii_post_interesting,
    z_post_positive = post_positive - x_ii_post_positive,
    z_post_agree = post_agree - x_ii_post_agree,
    z_post_align = post_align - x_ii_post_align
  ) %>% 
  mutate(
    across(starts_with("z_"), ~./sd(.))
  ) %>% 
  select(-starts_with("x_ii_")) %>% 
  rename_with(~paste0("x_", .), c(-ii, -jj, -kk, -starts_with("z_"))) %>% 
  left_join(df, ., by = c("ii", "jj", "kk"))

# Contrast code categorical predictor variables
dl <- dl %>% 
  mutate(
    post_framing = factor(
      post_framing, 
      levels = c("individualizing", "binding", "nonmoral")
    )
  )
contrasts(dl$post_framing) <- contr.sum(3)
df <- left_join(
  df, 
  dl %>% select(ii, x_post_framing = post_framing) %>% distinct(), 
  by = "ii"
)

# Standardize outcome variable
df <- dl %>% 
  transmute(
    ii, jj, kk, 
    z_post_share_index = (post_share_index - mean(post_share_index))/sd(post_share_index),
    z_post_share_index_public = (post_share_index_public - mean(post_share_index_public))/sd(post_share_index_public),
    z_post_share_index_private = (post_share_private - mean(post_share_private))/sd(post_share_private),
    z_post_share_index_offline = (post_share_offline - mean(post_share_offline))/sd(post_share_offline),
  ) %>% 
  left_join(df, by = c("ii", "jj", "kk"))

#post_share_public, # + post_like_public + post_share_private + post_share_offline
```


## Models
### Private sharing
```{r}
# Model 0 (Random Intercepts)
m0_fit_priv <- brm(
 z_post_share_index_private ~ 1 + (1|ii) + (1|jj) + (1|kk),
 data = df,
 chains = 8,
 iter = 1000,
 warmup = 750,
 seed = 6943546
)

# Model 1 (Headline-Level Predictors)
m1_fit_priv <- brm(
 z_post_share_index_private ~ 1 + z_kk_headline_believable + z_kk_headline_controversial + z_kk_headline_surprising + z_kk_headline_interesting + z_kk_headline_positive + z_kk_headline_true + z_headline_believable + z_headline_controversial + z_headline_surprising + z_headline_interesting + z_headline_positive + (1|ii) + (1|jj) + (1 + z_headline_believable + z_headline_controversial + z_headline_surprising + z_headline_interesting + z_headline_positive|kk),
 data = df,
 chains = 8,
 iter = 1000,
warmup = 750,
seed = 9103465
)

# Model 2 (Post-Level Predictors)
m2_fit_priv <- brm(
 z_post_share_index_private ~ 1 + z_ii_post_controversial + z_ii_post_surprising + z_ii_post_interesting + z_ii_post_positive + z_post_controversial + z_post_surprising + z_post_interesting + z_post_positive + (1 + z_post_controversial + z_post_surprising + z_post_interesting + z_post_positive|ii) + (1|jj) + (1|kk),
 data = df,
 chains = 8,
 iter = 1000,
 warmup = 750,
 seed = 3000256
)

# Model 3 (Person-/Post-Level Agreement/Alignment Predictors)
m3_fit_priv <- brm(
 z_post_share_index_private ~ 1 + z_post_agree*z_post_align + z_ii_post_agree*z_ii_post_align + (1 + z_post_agree*z_post_align|ii) + (1|jj) + (1|kk),
 data = df,
 chains = 8,
 iter = 1000,
 warmup = 750,
 seed = 3076878
)

# Model 4 (Person-Level Moral Predictors)
m4_fit_priv <- brm(
  z_post_share_index_private ~ 1 + x_post_framing*(z_jj_mfq_indi + z_jj_mfq_bind + z_jj_mfq_prop) + (1|jj) + (1 + x_post_framing*z_jj_mfq_indi + x_post_framing*(z_jj_mfq_indi + z_jj_mfq_bind + z_jj_mfq_prop)|kk),
  data = df,
  chains = 8,
  iter = 1500,
  warmup = 750,
  seed = 4962216,
  adapt_delta = 0.999
)

# Model 5 (Person-Level Ideological Predictor)
m5_fit_priv <- brm(
 z_post_share_index_private ~ 1 + x_post_framing*z_jj_conservatism + (1|jj) + (1 + x_post_framing*z_jj_conservatism|kk),
 data = df,
 chains = 8,
 iter = 1000,
 warmup = 750,
 seed = 6943546
)

# Model 6 (Model 4 with controls for inferences -- Main Model)
m6_fit_priv <- brm(
  z_post_share_index_private ~ 1 + z_kk_headline_true*x_post_framing*(z_jj_mfq_indi + z_jj_mfq_bind + z_jj_mfq_prop) + (1|jj) + (1 + x_post_framing*(z_jj_mfq_indi + z_jj_mfq_bind + z_jj_mfq_prop)|kk),
  data = df,
  chains = 8,
  iter = 1500,
  warmup = 750,
  seed = 4962216,
  adapt_delta = 0.999
)

# Assign folds for 10-fold cross-validation
set.seed(9735121)
df <- df %>% 
  distinct(jj) %>% 
  mutate(fold = sample.int(10, n(), replace = TRUE)) %>% 
  left_join(df, ., by = c("jj"))

# Run 10-fold cross-validation
plan(multisession)
m0_fit_priv <- add_criterion(
 m0_fit_priv,
 criterion = "kfold",
 chains = 1,
 folds = df$fold
)
m1_fit_priv <- add_criterion(
 m1_fit_priv,
 criterion = "kfold",
 chains = 1,
 folds = df$fold
)
m2_fit_priv <- add_criterion(
 m2_fit_priv,
 criterion = "kfold",
 chains = 1,
 folds = df$fold
)
m3_fit_priv <- add_criterion(
 m3_fit_priv,
 criterion = "kfold",
 chains = 1,
 folds = df$fold
)
m4_fit_priv <- add_criterion(
  m4_fit_priv,
  criterion = "kfold",
  chains = 1,
  folds = df$fold
)
m5_fit_priv <- add_criterion(
 m5_fit_priv,
 criterion = "kfold",
 chains = 1,
 folds = df$fold
)
m6_fit_priv <- add_criterion(
  m6_fit_priv,
  criterion = "kfold",
  chains = 1,
  folds = df$fold
)

plan("default")


# Calculate Bayesian R2
m0_fit_priv <- add_criterion(
 m0_fit_priv,
 criterion = "bayes_R2",
 re_formula = NA
)
m1_fit_priv <- add_criterion(
 m1_fit_priv,
 criterion = "bayes_R2",
 re_formula = NA
)
m2_fit_priv <- add_criterion(
 m2_fit_priv,
 criterion = "bayes_R2",
 re_formula = NA
)
m3_fit_priv <- add_criterion(
 m3_fit_priv,
 criterion = "bayes_R2",
 re_formula = NA
)
m4_fit_priv <- add_criterion(
  m4_fit_priv, 
  criterion = "bayes_R2",
  re_formula = NA
)
m5_fit_priv <- add_criterion(
 m5_fit_priv,
criterion = "bayes_R2",
 re_formula = NA
)
m6_fit_priv <- add_criterion(
  m6_fit_priv, 
  criterion = "bayes_R2",
  re_formula = NA
)


# Export ------------------------------------------------------------------

# Save results as .rds
write_rds(m0_fit_priv, "../results/m0_fit_priv.rds")
write_rds(m1_fit_priv, "../results/m1_fit_priv.rds")
write_rds(m2_fit_priv, "../results/m2_fit_priv.rds")
write_rds(m3_fit_priv, "../results/m3_fit_priv.rds")
write_rds(m4_fit_priv, "../results/m4_fit_priv.rds")
write_rds(m5_fit_priv, "../results/m5_fit_priv.rds")
write_rds(m6_fit_priv, "../results/m6_fit_priv.rds")
```


### Offline sharing
```{r}
# Model 0 (Random Intercepts)
m0_fit_off <- brm(
 z_post_share_index_offline ~ 1 + (1|ii) + (1|jj) + (1|kk),
 data = df,
 chains = 8,
 iter = 1000,
 warmup = 750,
 seed = 6943546
)

# Model 1 (Headline-Level Predictors)
m1_fit_off <- brm(
 z_post_share_index_offline ~ 1 + z_kk_headline_believable + z_kk_headline_controversial + z_kk_headline_surprising + z_kk_headline_interesting + z_kk_headline_positive + z_kk_headline_true + z_headline_believable + z_headline_controversial + z_headline_surprising + z_headline_interesting + z_headline_positive + (1|ii) + (1|jj) + (1 + z_headline_believable + z_headline_controversial + z_headline_surprising + z_headline_interesting + z_headline_positive|kk),
 data = df,
 chains = 8,
 iter = 1000,
warmup = 750,
seed = 9103465
)

# Model 2 (Post-Level Predictors)
m2_fit_off <- brm(
 z_post_share_index_offline ~ 1 + z_ii_post_controversial + z_ii_post_surprising + z_ii_post_interesting + z_ii_post_positive + z_post_controversial + z_post_surprising + z_post_interesting + z_post_positive + (1 + z_post_controversial + z_post_surprising + z_post_interesting + z_post_positive|ii) + (1|jj) + (1|kk),
 data = df,
 chains = 8,
 iter = 1000,
 warmup = 750,
 seed = 3000256
)

# Model 3 (Person-/Post-Level Agreement/Alignment Predictors)
m3_fit_off <- brm(
 z_post_share_index_offline ~ 1 + z_post_agree*z_post_align + z_ii_post_agree*z_ii_post_align + (1 + z_post_agree*z_post_align|ii) + (1|jj) + (1|kk),
 data = df,
 chains = 8,
 iter = 1000,
 warmup = 750,
 seed = 3076878
)

# Model 4 (Person-Level Moral Predictors)
m4_fit_off <- brm(
  z_post_share_index_offline ~ 1 + x_post_framing*(z_jj_mfq_indi + z_jj_mfq_bind + z_jj_mfq_prop) + (1|jj) + (1 + x_post_framing*(z_jj_mfq_indi + z_jj_mfq_bind + z_jj_mfq_prop)|kk),
  data = df,
  chains = 8,
  iter = 1500,
  warmup = 750,
  seed = 4962216,
  adapt_delta = 0.999
)

# Model 5 (Person-Level Ideological Predictor)
m5_fit_off <- brm(
 z_post_share_index_offline ~ 1 + x_post_framing*z_jj_conservatism + (1|jj) + (1 + x_post_framing*z_jj_conservatism|kk),
 data = df,
 chains = 8,
 iter = 1000,
 warmup = 750,
 seed = 6943546
)

# Model 6 (Model 4 with controls for inferences)
m6_fit_off <- brm(
  z_post_share_index_offline ~ 1 + z_kk_headline_true*x_post_framing*(z_jj_mfq_indi + z_jj_mfq_bind + z_jj_mfq_prop) + (1|jj) + (1 + x_post_framing*(z_jj_mfq_indi + z_jj_mfq_bind + z_jj_mfq_prop)|kk),
  data = df,
  chains = 8,
  iter = 1500,
  warmup = 750,
  seed = 4962216,
  adapt_delta = 0.999
)

# Assign folds for 10-fold cross-validation
set.seed(9735121)
df <- df %>% 
  distinct(jj) %>% 
  mutate(fold = sample.int(10, n(), replace = TRUE)) %>% 
  left_join(df, ., by = c("jj"))

# Run 10-fold cross-validation
plan(multisession)
m0_fit_off <- add_criterion(
 m0_fit_off,
 criterion = "kfold",
 chains = 1,
 folds = df$fold
)
m1_fit_off <- add_criterion(
 m1_fit_off,
 criterion = "kfold",
 chains = 1,
 folds = df$fold
)
m2_fit_off <- add_criterion(
 m2_fit_off,
 criterion = "kfold",
 chains = 1,
 folds = df$fold
)
m3_fit_off <- add_criterion(
 m3_fit_off,
 criterion = "kfold",
 chains = 1,
 folds = df$fold
)
m4_fit_off <- add_criterion(
  m4_fit_off,
  criterion = "kfold",
  chains = 1,
  folds = df$fold
)
m5_fit_off <- add_criterion(
 m5_fit_off,
 criterion = "kfold",
 chains = 1,
 folds = df$fold
)
m6_fit_off <- add_criterion(
  m6_fit_off,
  criterion = "kfold",
  chains = 1,
  folds = df$fold
)

plan("default")

# Calculate Bayesian R2
m0_fit_off <- add_criterion(
 m0_fit_off,
 criterion = "bayes_R2",
 re_formula = NA
)
m1_fit_off <- add_criterion(
 m1_fit_off,
 criterion = "bayes_R2",
 re_formula = NA
)
m2_fit_off <- add_criterion(
 m2_fit_off,
 criterion = "bayes_R2",
 re_formula = NA
)
m3_fit_off <- add_criterion(
 m3_fit_off,
 criterion = "bayes_R2",
 re_formula = NA
)
m4_fit_off <- add_criterion(
  m4_fit_off, 
  criterion = "bayes_R2",
  re_formula = NA
)
m5_fit_off <- add_criterion(
 m5_fit_off,
criterion = "bayes_R2",
 re_formula = NA
)
m6_fit_off <- add_criterion(
  m6_fit_off, 
  criterion = "bayes_R2",
  re_formula = NA
)


# Export ------------------------------------------------------------------

# Save results as .rds
write_rds(m0_fit_off, "../results/m0_fit_off.rds")
write_rds(m1_fit_off, "../results/m1_fit_off.rds")
write_rds(m2_fit_off, "../results/m2_fit_off.rds")
write_rds(m3_fit_off, "../results/m3_fit_off.rds")
write_rds(m4_fit_off, "../results/m4_fit_off.rds")
write_rds(m5_fit_off, "../results/m5_fit_off.rds")
write_rds(m6_fit_off, "../results/m6_fit_off.rds")
```


### Public sharing
```{r}
# Model 0 (Random Intercepts)
m0_fit_public <- brm(
 z_post_share_index_public ~ 1 + (1|ii) + (1|jj) + (1|kk),
 data = df,
 chains = 8,
 iter = 1000,
 warmup = 750,
 seed = 6943546
)

# Model 1 (Headline-Level Predictors)
m1_fit_public <- brm(
 z_post_share_index_public ~ 1 + z_kk_headline_believable + z_kk_headline_controversial + z_kk_headline_surprising + z_kk_headline_interesting + z_kk_headline_positive + z_kk_headline_true + z_headline_believable + z_headline_controversial + z_headline_surprising + z_headline_interesting + z_headline_positive + (1|ii) + (1|jj) + (1 + z_headline_believable + z_headline_controversial + z_headline_surprising + z_headline_interesting + z_headline_positive|kk),
 data = df,
 chains = 8,
 iter = 1000,
warmup = 750,
seed = 9103465
)

# Model 2 (Post-Level Predictors)
m2_fit_public <- brm(
 z_post_share_index_public ~ 1 + z_ii_post_controversial + z_ii_post_surprising + z_ii_post_interesting + z_ii_post_positive + z_post_controversial + z_post_surprising + z_post_interesting + z_post_positive + (1 + z_post_controversial + z_post_surprising + z_post_interesting + z_post_positive|ii) + (1|jj) + (1|kk),
 data = df,
 chains = 8,
 iter = 1000,
 warmup = 750,
 seed = 3000256
)

# Model 3 (Person-/Post-Level Agreement/Alignment Predictors)
m3_fit_public <- brm(
 z_post_share_index_public ~ 1 + z_post_agree*z_post_align + z_ii_post_agree*z_ii_post_align + (1 + z_post_agree*z_post_align|ii) + (1|jj) + (1|kk),
 data = df,
 chains = 8,
 iter = 1000,
 warmup = 750,
 seed = 3076878
)

# Model 4 (Person-Level Moral Predictors)
m4_fit_public <- brm(
  z_post_share_index_public ~ 1 + x_post_framing*(z_jj_mfq_indi + z_jj_mfq_bind + z_jj_mfq_prop) + (1|jj) + (1 + x_post_framing*(z_jj_mfq_indi + z_jj_mfq_bind + z_jj_mfq_prop)|kk),
  data = df,
  chains = 8,
  iter = 1500,
  warmup = 750,
  seed = 4962216,
  adapt_delta = 0.999
)

# Model 5 (Person-Level Ideological Predictor)
m5_fit_public <- brm(
 z_post_share_index_public ~ 1 + x_post_framing*z_jj_conservatism + (1|jj) + (1 + x_post_framing*z_jj_conservatism|kk),
 data = df,
 chains = 8,
 iter = 1000,
 warmup = 750,
 seed = 6943546
)

# Model 6 (Model 4 with controls for inferences)
m6_fit_public <- brm(
  z_post_share_index_public ~ 1 + z_kk_headline_true*x_post_framing*(z_jj_mfq_indi + z_jj_mfq_bind + z_jj_mfq_prop) + (1|jj) + (1 + x_post_framing*(z_jj_mfq_indi + z_jj_mfq_bind + z_jj_mfq_prop)|kk),
  data = df,
  chains = 8,
  iter = 1500,
  warmup = 750,
  seed = 4962216,
  adapt_delta = 0.999
)

# Assign folds for 10-fold cross-validation
set.seed(9735121)
df <- df %>% 
  distinct(jj) %>% 
  mutate(fold = sample.int(10, n(), replace = TRUE)) %>% 
  left_join(df, ., by = c("jj"))

# Run 10-fold cross-validation
plan(multisession)
m0_fit_public <- add_criterion(
 m0_fit_public,
 criterion = "kfold",
 chains = 1,
 folds = df$fold
)
m1_fit_public <- add_criterion(
 m1_fit_public,
 criterion = "kfold",
 chains = 1,
 folds = df$fold
)
m2_fit_public <- add_criterion(
 m2_fit_public,
 criterion = "kfold",
 chains = 1,
 folds = df$fold
)
m3_fit_public <- add_criterion(
 m3_fit_public,
 criterion = "kfold",
 chains = 1,
 folds = df$fold
)
m4_fit_public <- add_criterion(
  m4_fit_public,
  criterion = "kfold",
  chains = 1,
  folds = df$fold
)
m5_fit_public <- add_criterion(
 m5_fit_public,
 criterion = "kfold",
 chains = 1,
 folds = df$fold
)
m6_fit_public <- add_criterion(
  m6_fit_public,
  criterion = "kfold",
  chains = 1,
  folds = df$fold
)

plan("default")

# Calculate Bayesian R2
m0_fit_public <- add_criterion(
 m0_fit_public,
 criterion = "bayes_R2",
 re_formula = NA
)
m1_fit_public <- add_criterion(
 m1_fit_public,
 criterion = "bayes_R2",
 re_formula = NA
)
m2_fit_public <- add_criterion(
 m2_fit_public,
 criterion = "bayes_R2",
 re_formula = NA
)
m3_fit_public <- add_criterion(
 m3_fit_public,
 criterion = "bayes_R2",
 re_formula = NA
)
m4_fit_public <- add_criterion(
  m4_fit_public, 
  criterion = "bayes_R2",
  re_formula = NA
)
m5_fit_public <- add_criterion(
 m5_fit_public,
criterion = "bayes_R2",
 re_formula = NA
)
m6_fit_public <- add_criterion(
  m6_fit_public, 
  criterion = "bayes_R2",
  re_formula = NA
)


# Export ------------------------------------------------------------------

# Save results as .rds
write_rds(m0_fit_public, "../results/m0_fit_public.rds")
write_rds(m1_fit_public, "../results/m1_fit_public.rds")
write_rds(m2_fit_public, "../results/m2_fit_public.rds")
write_rds(m3_fit_public, "../results/m3_fit_public.rds")
write_rds(m4_fit_public, "../results/m4_fit_public.rds")
write_rds(m5_fit_public, "../results/m5_fit_public.rds")
write_rds(m6_fit_public, "../results/m6_fit_public.rds")
```


## Model comparisons
### Load models
```{r}
m0_fit_public <- readRDS("../results/m0_fit_public.rds")
m1_fit_public <- readRDS("../results/m1_fit_public.rds")
m2_fit_public <- readRDS("../results/m2_fit_public.rds")
m3_fit_public <- readRDS("../results/m3_fit_public.rds")
m4_fit_public <- readRDS("../results/m4_fit_public.rds")
m5_fit_public <- readRDS("../results/m5_fit_public.rds")
m6_fit_public <- readRDS( "../results/m6_fit_public.rds")

m0_fit_priv <- readRDS("../results/m0_fit_priv.rds")
m1_fit_priv <- readRDS("../results/m1_fit_priv.rds")
m2_fit_priv <- readRDS("../results/m2_fit_priv.rds")
m3_fit_priv <- readRDS("../results/m3_fit_priv.rds")
m4_fit_priv <- readRDS("../results/m4_fit_priv.rds")
m5_fit_priv <- readRDS("../results/m5_fit_priv.rds")
m6_fit_priv <- readRDS( "../results/m6_fit_priv.rds")

m0_fit_off <- readRDS("../results/m0_fit_off.rds")
m1_fit_off <- readRDS("../results/m1_fit_off.rds")
m2_fit_off <- readRDS("../results/m2_fit_off.rds")
m3_fit_off <- readRDS("../results/m3_fit_off.rds")
m4_fit_off <- readRDS("../results/m4_fit_off.rds")
m5_fit_off <- readRDS("../results/m5_fit_off.rds")
m6_fit_off <- readRDS( "../results/m6_fit_off.rds")

# load original model with averaged ratings
m4_fit <- readRDS( "../results/m4_fit.rds")
m6_fit <- readRDS( "../results/m6_fit.rds")
m6_ver_results <- readRDS( "../results/m6_effects_ver.rds")
```


### Print results
The results show the difference in predictive power (pairwise contrast) across models for each of the 3 DVs (private sharing, offline sharing, public sharing)
```{r}
###### Adjust for the two models!
# Initialize models
results <- crossing(
    model0 = paste0("M", 0:5),
    model1 = paste0("M", 0:5)
  ) %>% 
    mutate(
      fit0 = map(model0, ~read_rds(paste0("../results/", str_to_lower(.), "_fit_priv.rds"))),
      fit1 = map(model1, ~read_rds(paste0("../results/", str_to_lower(.), "_fit_priv.rds")))
    )

# Calculate ELPD differences
results <- results %>% 
  mutate(
    ELPD = map2(
      fit0, 
      fit1, 
      ~loo_compare(.x, .y, criterion = "kfold") %>% 
        as.data.frame() %>%
        rownames_to_column("model")
    )
  ) %>% 
  unnest(ELPD) %>% 
  group_by(model0, model1) %>% 
  dplyr::summarize(
    elpd_diff = elpd_diff[model == ".x"] - elpd_diff[model == ".y"],
    elpd_se_diff = max(se_diff)
  ) %>% 
  ungroup() %>% 
  left_join(
    results %>% 
      mutate(
        R2 = map(
          fit0, 
          ~bayes_R2(., robust = T) %>% as_tibble()
        )
      ) %>% 
      unnest(R2) %>% 
      transmute(
        model0,
        r2 = Estimate,
        r2_l95 = Q2.5,
        r2_u95 = Q97.5
      ) %>% 
      distinct(),
    by = "model0"
  )

#combine comparisons
results_comparison_priv <- results %>% mutate(z = elpd_diff / elpd_se_diff)
print(results_comparison_priv)
  
# Save results as .rds
write_rds(results_comparison_priv, "../results/comparison_priv.rds")

results <- crossing(
    model0 = paste0("M", 0:5),
    model1 = paste0("M", 0:5)
  ) %>% 
    mutate(
      fit0 = map(model0, ~read_rds(paste0("../results/", str_to_lower(.), "_fit_off.rds"))),
      fit1 = map(model1, ~read_rds(paste0("../results/", str_to_lower(.), "_fit_off.rds")))
    )

# Calculate ELPD differences
results <- results %>% 
  mutate(
    ELPD = map2(
      fit0, 
      fit1, 
      ~loo_compare(.x, .y, criterion = "kfold") %>% 
        as.data.frame() %>%
        rownames_to_column("model")
    )
  ) %>% 
  unnest(ELPD) %>% 
  group_by(model0, model1) %>% 
  dplyr::summarize(
    elpd_diff = elpd_diff[model == ".x"] - elpd_diff[model == ".y"],
    elpd_se_diff = max(se_diff)
  ) %>% 
  ungroup() %>% 
  left_join(
    results %>% 
      mutate(
        R2 = map(
          fit0, 
          ~bayes_R2(., robust = T) %>% as_tibble()
        )
      ) %>% 
      unnest(R2) %>% 
      transmute(
        model0,
        r2 = Estimate,
        r2_l95 = Q2.5,
        r2_u95 = Q97.5
      ) %>% 
      distinct(),
    by = "model0"
  )

#combine comparisons
results_comparison_off <- results %>% mutate(z = elpd_diff / elpd_se_diff)
print(results_comparison_off)

# Save results as .rds
write_rds(results_comparison_off, "../results/comparison_off.rds")


results <- crossing(
    model0 = paste0("M", 0:5),
    model1 = paste0("M", 0:5)
  ) %>% 
    mutate(
      fit0 = map(model0, ~read_rds(paste0("../results/", str_to_lower(.), "_fit_public.rds"))),
      fit1 = map(model1, ~read_rds(paste0("../results/", str_to_lower(.), "_fit_public.rds")))
    )

# Calculate ELPD differences
results <- results %>% 
  mutate(
    ELPD = map2(
      fit0, 
      fit1, 
      ~loo_compare(.x, .y, criterion = "kfold") %>% 
        as.data.frame() %>%
        rownames_to_column("model")
    )
  ) %>% 
  unnest(ELPD) %>% 
  group_by(model0, model1) %>% 
  dplyr::summarize(
    elpd_diff = elpd_diff[model == ".x"] - elpd_diff[model == ".y"],
    elpd_se_diff = max(se_diff)
  ) %>% 
  ungroup() %>% 
  left_join(
    results %>% 
      mutate(
        R2 = map(
          fit0, 
          ~bayes_R2(., robust = T) %>% as_tibble()
        )
      ) %>% 
      unnest(R2) %>% 
      transmute(
        model0,
        r2 = Estimate,
        r2_l95 = Q2.5,
        r2_u95 = Q97.5
      ) %>% 
      distinct(),
    by = "model0"
  )

#combine comparisons
results_comparison_public <- results %>% mutate(z = elpd_diff / elpd_se_diff)
print(results_comparison_public)
  
# Save results as .rds
write_rds(results_comparison_public, "../results/comparison_public.rds")
```


### M6 (Main model: Moral alignment x veracity)
This adds the veracity interaction to the main model (vs only controlling for veracity) for all DVs (private sharing, offline, public, total/averaged)
```{r}
  # Extract coefficients: Model 6 (main model + control)
m6_results_priv <- m6_fit_priv %>% 
  spread_draws(
      b_z_jj_mfq_indi,
      b_z_jj_mfq_bind,
      b_z_jj_mfq_prop,
      `b_x_post_framing1:z_jj_mfq_indi`,
      `b_x_post_framing2:z_jj_mfq_indi`,
      `b_x_post_framing1:z_jj_mfq_bind`,
      `b_x_post_framing2:z_jj_mfq_bind`,
      `b_x_post_framing1:z_jj_mfq_prop`,
      `b_x_post_framing2:z_jj_mfq_prop`,
      `b_z_kk_headline_true:x_post_framing1:z_jj_mfq_indi`,
      `b_z_kk_headline_true:x_post_framing2:z_jj_mfq_indi`,
      `b_z_kk_headline_true:x_post_framing1:z_jj_mfq_bind`,
      `b_z_kk_headline_true:x_post_framing2:z_jj_mfq_bind`,
      `b_z_kk_headline_true:x_post_framing1:z_jj_mfq_prop`,
      `b_z_kk_headline_true:x_post_framing2:z_jj_mfq_prop`,
    ) %>% 
    transmute(
      .chain, .iteration, .draw,
      b_indi_indi = b_z_jj_mfq_indi + 1 * `b_x_post_framing1:z_jj_mfq_indi`,
      b_indi_bind = b_z_jj_mfq_indi + 1 * `b_x_post_framing2:z_jj_mfq_indi`,
      b_indi_nonm = b_z_jj_mfq_indi + -1 * `b_x_post_framing1:z_jj_mfq_indi` + -1 * `b_x_post_framing2:z_jj_mfq_indi`,
      b_bind_indi = b_z_jj_mfq_bind + 1 * `b_x_post_framing1:z_jj_mfq_bind`,
      b_bind_bind = b_z_jj_mfq_bind + 1 * `b_x_post_framing2:z_jj_mfq_bind`,
      b_bind_nonm = b_z_jj_mfq_bind + -1 * `b_x_post_framing1:z_jj_mfq_bind` + -1 * `b_x_post_framing2:z_jj_mfq_bind`,
      b_prop_indi = b_z_jj_mfq_prop + 1 * `b_x_post_framing1:z_jj_mfq_prop`,
      b_prop_bind = b_z_jj_mfq_prop + 1 * `b_x_post_framing2:z_jj_mfq_prop`,
      b_prop_nonm = b_z_jj_mfq_prop + -1 * `b_x_post_framing1:z_jj_mfq_prop` + -1 * `b_x_post_framing2:z_jj_mfq_prop`,
      d_indi_indi_bind = b_indi_indi - b_indi_bind,
      d_indi_indi_nonm = b_indi_indi - b_indi_nonm,
      d_indi_bind_nonm = b_indi_bind - b_indi_nonm,
      d_bind_bind_indi = b_bind_bind - b_bind_indi,
      d_bind_bind_nonm = b_bind_bind - b_bind_nonm,
      d_bind_ind_nonm = b_bind_indi - b_bind_nonm,
      
      b_indi_indi_true = b_z_jj_mfq_indi + 1 * (`b_x_post_framing1:z_jj_mfq_indi` + `b_z_kk_headline_true:x_post_framing1:z_jj_mfq_indi`),
      b_indi_bind_true = b_z_jj_mfq_indi + 1 * (`b_x_post_framing2:z_jj_mfq_indi` + `b_z_kk_headline_true:x_post_framing2:z_jj_mfq_indi`),
      b_indi_nonm_true = b_z_jj_mfq_indi + -1 * (`b_x_post_framing1:z_jj_mfq_indi` + `b_z_kk_headline_true:x_post_framing1:z_jj_mfq_indi`) + -1 * (`b_x_post_framing2:z_jj_mfq_indi` + `b_z_kk_headline_true:x_post_framing2:z_jj_mfq_indi`),
      b_bind_indi_true = b_z_jj_mfq_bind + 1 * (`b_x_post_framing1:z_jj_mfq_bind` + `b_z_kk_headline_true:x_post_framing1:z_jj_mfq_bind`),
      b_bind_bind_true = b_z_jj_mfq_bind + 1 * (`b_x_post_framing2:z_jj_mfq_bind` + `b_z_kk_headline_true:x_post_framing2:z_jj_mfq_bind`),
      b_bind_nonm_true = b_z_jj_mfq_bind + -1 * (`b_x_post_framing1:z_jj_mfq_bind` + `b_z_kk_headline_true:x_post_framing1:z_jj_mfq_bind`) + -1 * (`b_x_post_framing2:z_jj_mfq_bind` + `b_z_kk_headline_true:x_post_framing2:z_jj_mfq_bind`),
      b_prop_indi_true = b_z_jj_mfq_prop + 1 * (`b_x_post_framing1:z_jj_mfq_prop` + `b_z_kk_headline_true:x_post_framing1:z_jj_mfq_prop`),
      b_prop_bind_true = b_z_jj_mfq_prop + 1 * (`b_x_post_framing2:z_jj_mfq_prop` + `b_z_kk_headline_true:x_post_framing2:z_jj_mfq_prop`),
      b_prop_nonm_true = b_z_jj_mfq_prop + -1 * (`b_x_post_framing1:z_jj_mfq_prop` + `b_z_kk_headline_true:x_post_framing1:z_jj_mfq_prop`) + -1 * (`b_x_post_framing2:z_jj_mfq_prop` + `b_z_kk_headline_true:x_post_framing2:z_jj_mfq_prop`),
      d_indi_indi_bind_true = b_indi_indi_true - b_indi_bind_true,
      d_indi_indi_nonm_true = b_indi_indi_true - b_indi_nonm_true,
      d_indi_bind_nonm_true = b_indi_bind_true - b_indi_nonm_true,
      d_bind_bind_indi_true = b_bind_bind_true - b_bind_indi_true,
      d_bind_bind_nonm_true = b_bind_bind_true - b_bind_nonm_true,
      d_bind_ind_nonm_true = b_bind_indi_true - b_bind_nonm_true,
      
    ) %>% dplyr::select(starts_with("d_"), .chain, .iteration, .draw) %>%
    pivot_longer(c(-.chain, -.iteration, -.draw)) %>% 
    group_by(name) %>% 
    median_qi(value) %>% 
    mutate(across(where(is.numeric), numform::f_num, digits = 2, retain.leading.zero = T))
write_rds(m6_results_priv, "../results/m6_effects_priv.rds")
print(m6_results_priv)


m6_results_off <- m6_fit_off %>% 
  spread_draws(
      b_z_jj_mfq_indi,
      b_z_jj_mfq_bind,
      b_z_jj_mfq_prop,
      `b_x_post_framing1:z_jj_mfq_indi`,
      `b_x_post_framing2:z_jj_mfq_indi`,
      `b_x_post_framing1:z_jj_mfq_bind`,
      `b_x_post_framing2:z_jj_mfq_bind`,
      `b_x_post_framing1:z_jj_mfq_prop`,
      `b_x_post_framing2:z_jj_mfq_prop`,
      `b_z_kk_headline_true:x_post_framing1:z_jj_mfq_indi`,
      `b_z_kk_headline_true:x_post_framing2:z_jj_mfq_indi`,
      `b_z_kk_headline_true:x_post_framing1:z_jj_mfq_bind`,
      `b_z_kk_headline_true:x_post_framing2:z_jj_mfq_bind`,
      `b_z_kk_headline_true:x_post_framing1:z_jj_mfq_prop`,
      `b_z_kk_headline_true:x_post_framing2:z_jj_mfq_prop`,
    ) %>% 
    transmute(
      .chain, .iteration, .draw,
      b_indi_indi = b_z_jj_mfq_indi + 1 * `b_x_post_framing1:z_jj_mfq_indi`,
      b_indi_bind = b_z_jj_mfq_indi + 1 * `b_x_post_framing2:z_jj_mfq_indi`,
      b_indi_nonm = b_z_jj_mfq_indi + -1 * `b_x_post_framing1:z_jj_mfq_indi` + -1 * `b_x_post_framing2:z_jj_mfq_indi`,
      b_bind_indi = b_z_jj_mfq_bind + 1 * `b_x_post_framing1:z_jj_mfq_bind`,
      b_bind_bind = b_z_jj_mfq_bind + 1 * `b_x_post_framing2:z_jj_mfq_bind`,
      b_bind_nonm = b_z_jj_mfq_bind + -1 * `b_x_post_framing1:z_jj_mfq_bind` + -1 * `b_x_post_framing2:z_jj_mfq_bind`,
      b_prop_indi = b_z_jj_mfq_prop + 1 * `b_x_post_framing1:z_jj_mfq_prop`,
      b_prop_bind = b_z_jj_mfq_prop + 1 * `b_x_post_framing2:z_jj_mfq_prop`,
      b_prop_nonm = b_z_jj_mfq_prop + -1 * `b_x_post_framing1:z_jj_mfq_prop` + -1 * `b_x_post_framing2:z_jj_mfq_prop`,
      d_indi_indi_bind = b_indi_indi - b_indi_bind,
      d_indi_indi_nonm = b_indi_indi - b_indi_nonm,
      d_indi_bind_nonm = b_indi_bind - b_indi_nonm,
      d_bind_bind_indi = b_bind_bind - b_bind_indi,
      d_bind_bind_nonm = b_bind_bind - b_bind_nonm,
      d_bind_ind_nonm = b_bind_indi - b_bind_nonm,
      
      b_indi_indi_true = b_z_jj_mfq_indi + 1 * (`b_x_post_framing1:z_jj_mfq_indi` + `b_z_kk_headline_true:x_post_framing1:z_jj_mfq_indi`),
      b_indi_bind_true = b_z_jj_mfq_indi + 1 * (`b_x_post_framing2:z_jj_mfq_indi` + `b_z_kk_headline_true:x_post_framing2:z_jj_mfq_indi`),
      b_indi_nonm_true = b_z_jj_mfq_indi + -1 * (`b_x_post_framing1:z_jj_mfq_indi` + `b_z_kk_headline_true:x_post_framing1:z_jj_mfq_indi`) + -1 * (`b_x_post_framing2:z_jj_mfq_indi` + `b_z_kk_headline_true:x_post_framing2:z_jj_mfq_indi`),
      b_bind_indi_true = b_z_jj_mfq_bind + 1 * (`b_x_post_framing1:z_jj_mfq_bind` + `b_z_kk_headline_true:x_post_framing1:z_jj_mfq_bind`),
      b_bind_bind_true = b_z_jj_mfq_bind + 1 * (`b_x_post_framing2:z_jj_mfq_bind` + `b_z_kk_headline_true:x_post_framing2:z_jj_mfq_bind`),
      b_bind_nonm_true = b_z_jj_mfq_bind + -1 * (`b_x_post_framing1:z_jj_mfq_bind` + `b_z_kk_headline_true:x_post_framing1:z_jj_mfq_bind`) + -1 * (`b_x_post_framing2:z_jj_mfq_bind` + `b_z_kk_headline_true:x_post_framing2:z_jj_mfq_bind`),
      b_prop_indi_true = b_z_jj_mfq_prop + 1 * (`b_x_post_framing1:z_jj_mfq_prop` + `b_z_kk_headline_true:x_post_framing1:z_jj_mfq_prop`),
      b_prop_bind_true = b_z_jj_mfq_prop + 1 * (`b_x_post_framing2:z_jj_mfq_prop` + `b_z_kk_headline_true:x_post_framing2:z_jj_mfq_prop`),
      b_prop_nonm_true = b_z_jj_mfq_prop + -1 * (`b_x_post_framing1:z_jj_mfq_prop` + `b_z_kk_headline_true:x_post_framing1:z_jj_mfq_prop`) + -1 * (`b_x_post_framing2:z_jj_mfq_prop` + `b_z_kk_headline_true:x_post_framing2:z_jj_mfq_prop`),
      d_indi_indi_bind_true = b_indi_indi_true - b_indi_bind_true,
      d_indi_indi_nonm_true = b_indi_indi_true - b_indi_nonm_true,
      d_indi_bind_nonm_true = b_indi_bind_true - b_indi_nonm_true,
      d_bind_bind_indi_true = b_bind_bind_true - b_bind_indi_true,
      d_bind_bind_nonm_true = b_bind_bind_true - b_bind_nonm_true,
      d_bind_ind_nonm_true = b_bind_indi_true - b_bind_nonm_true,
      
    ) %>% dplyr::select(starts_with("d_"), .chain, .iteration, .draw) %>%
    pivot_longer(c(-.chain, -.iteration, -.draw)) %>% 
    group_by(name) %>% 
    median_qi(value) %>% 
    mutate(across(where(is.numeric), numform::f_num, digits = 2, retain.leading.zero = T))
write_rds(m6_results_off, "../results/m6_effects_off.rds")
print(m6_results_off)


m6_results_public <- m6_fit_public %>% 
  spread_draws(
      b_z_jj_mfq_indi,
      b_z_jj_mfq_bind,
      b_z_jj_mfq_prop,
      `b_x_post_framing1:z_jj_mfq_indi`,
      `b_x_post_framing2:z_jj_mfq_indi`,
      `b_x_post_framing1:z_jj_mfq_bind`,
      `b_x_post_framing2:z_jj_mfq_bind`,
      `b_x_post_framing1:z_jj_mfq_prop`,
      `b_x_post_framing2:z_jj_mfq_prop`,
      `b_z_kk_headline_true:x_post_framing1:z_jj_mfq_indi`,
      `b_z_kk_headline_true:x_post_framing2:z_jj_mfq_indi`,
      `b_z_kk_headline_true:x_post_framing1:z_jj_mfq_bind`,
      `b_z_kk_headline_true:x_post_framing2:z_jj_mfq_bind`,
      `b_z_kk_headline_true:x_post_framing1:z_jj_mfq_prop`,
      `b_z_kk_headline_true:x_post_framing2:z_jj_mfq_prop`,
    ) %>% 
    transmute(
      .chain, .iteration, .draw,
      b_indi_indi = b_z_jj_mfq_indi + 1 * `b_x_post_framing1:z_jj_mfq_indi`,
      b_indi_bind = b_z_jj_mfq_indi + 1 * `b_x_post_framing2:z_jj_mfq_indi`,
      b_indi_nonm = b_z_jj_mfq_indi + -1 * `b_x_post_framing1:z_jj_mfq_indi` + -1 * `b_x_post_framing2:z_jj_mfq_indi`,
      b_bind_indi = b_z_jj_mfq_bind + 1 * `b_x_post_framing1:z_jj_mfq_bind`,
      b_bind_bind = b_z_jj_mfq_bind + 1 * `b_x_post_framing2:z_jj_mfq_bind`,
      b_bind_nonm = b_z_jj_mfq_bind + -1 * `b_x_post_framing1:z_jj_mfq_bind` + -1 * `b_x_post_framing2:z_jj_mfq_bind`,
      b_prop_indi = b_z_jj_mfq_prop + 1 * `b_x_post_framing1:z_jj_mfq_prop`,
      b_prop_bind = b_z_jj_mfq_prop + 1 * `b_x_post_framing2:z_jj_mfq_prop`,
      b_prop_nonm = b_z_jj_mfq_prop + -1 * `b_x_post_framing1:z_jj_mfq_prop` + -1 * `b_x_post_framing2:z_jj_mfq_prop`,
      d_indi_indi_bind = b_indi_indi - b_indi_bind,
      d_indi_indi_nonm = b_indi_indi - b_indi_nonm,
      d_indi_bind_nonm = b_indi_bind - b_indi_nonm,
      d_bind_bind_indi = b_bind_bind - b_bind_indi,
      d_bind_bind_nonm = b_bind_bind - b_bind_nonm,
      d_bind_ind_nonm = b_bind_indi - b_bind_nonm,
      
      b_indi_indi_true = b_z_jj_mfq_indi + 1 * (`b_x_post_framing1:z_jj_mfq_indi` + `b_z_kk_headline_true:x_post_framing1:z_jj_mfq_indi`),
      b_indi_bind_true = b_z_jj_mfq_indi + 1 * (`b_x_post_framing2:z_jj_mfq_indi` + `b_z_kk_headline_true:x_post_framing2:z_jj_mfq_indi`),
      b_indi_nonm_true = b_z_jj_mfq_indi + -1 * (`b_x_post_framing1:z_jj_mfq_indi` + `b_z_kk_headline_true:x_post_framing1:z_jj_mfq_indi`) + -1 * (`b_x_post_framing2:z_jj_mfq_indi` + `b_z_kk_headline_true:x_post_framing2:z_jj_mfq_indi`),
      b_bind_indi_true = b_z_jj_mfq_bind + 1 * (`b_x_post_framing1:z_jj_mfq_bind` + `b_z_kk_headline_true:x_post_framing1:z_jj_mfq_bind`),
      b_bind_bind_true = b_z_jj_mfq_bind + 1 * (`b_x_post_framing2:z_jj_mfq_bind` + `b_z_kk_headline_true:x_post_framing2:z_jj_mfq_bind`),
      b_bind_nonm_true = b_z_jj_mfq_bind + -1 * (`b_x_post_framing1:z_jj_mfq_bind` + `b_z_kk_headline_true:x_post_framing1:z_jj_mfq_bind`) + -1 * (`b_x_post_framing2:z_jj_mfq_bind` + `b_z_kk_headline_true:x_post_framing2:z_jj_mfq_bind`),
      b_prop_indi_true = b_z_jj_mfq_prop + 1 * (`b_x_post_framing1:z_jj_mfq_prop` + `b_z_kk_headline_true:x_post_framing1:z_jj_mfq_prop`),
      b_prop_bind_true = b_z_jj_mfq_prop + 1 * (`b_x_post_framing2:z_jj_mfq_prop` + `b_z_kk_headline_true:x_post_framing2:z_jj_mfq_prop`),
      b_prop_nonm_true = b_z_jj_mfq_prop + -1 * (`b_x_post_framing1:z_jj_mfq_prop` + `b_z_kk_headline_true:x_post_framing1:z_jj_mfq_prop`) + -1 * (`b_x_post_framing2:z_jj_mfq_prop` + `b_z_kk_headline_true:x_post_framing2:z_jj_mfq_prop`),
      d_indi_indi_bind_true = b_indi_indi_true - b_indi_bind_true,
      d_indi_indi_nonm_true = b_indi_indi_true - b_indi_nonm_true,
      d_indi_bind_nonm_true = b_indi_bind_true - b_indi_nonm_true,
      d_bind_bind_indi_true = b_bind_bind_true - b_bind_indi_true,
      d_bind_bind_nonm_true = b_bind_bind_true - b_bind_nonm_true,
      d_bind_ind_nonm_true = b_bind_indi_true - b_bind_nonm_true,
      
    ) %>% dplyr::select(starts_with("d_"), .chain, .iteration, .draw) %>%
    pivot_longer(c(-.chain, -.iteration, -.draw)) %>% 
    group_by(name) %>% 
    median_qi(value) %>% 
    mutate(across(where(is.numeric), numform::f_num, digits = 2, retain.leading.zero = T))
write_rds(m6_results_public, "../results/m6_effects_public.rds")
print(m6_results_public)


print(m6_ver_results)
```